Machine Learning Methods for Site-specific Input Management

### 2022-02-08 Codes/PrepareResults.rmd

knitr::opts_chunk$set(
  cache = TRUE
)
```
```{r packages, cache = FALSE, include = FALSE}
# === packages ===#
# --- data wrangling--- #
library(sf)
library(data.table)
library(tidyverse)

# --- figure making --- #
library(ggbrace)
library(RColorBrewer)
library(patchwork)
library(ggplot2)
library(ggthemes)
library(viridis)
library(ggpubr)
library(gridExtra)
library(DiagrammeR)

# --- table making --- #
library(flextable)
library(officer)
library(officedown)
library(modelsummary)
library(latex2exp)
```

@@

theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain", family = "Cambria"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain", family = "Cambria"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain", family = "Cambria"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain", family = "Cambria"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain", family = "Cambria"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain", family = "Cambria"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)

set_flextable_defaults(
  font.family = "Cambria"
  )
```

@@

```{r}
variogram_tb <-
  data.frame(
    Parameters = c("ymax_ij", "alpha_ij", "beta_ij", "varepsilon_ij"),
    Range = c(400, 400, 400, 400),
    Mean = c(12000, -0.5, format(c(0, 0))),
    Nugget = format(c(0, 0, 0, 0)),
    Sill = c(2000000, 0.02, format(1, nsmall = 1), 0.015)
  ) %>%
  flextable() %>%
  compose(i = 1, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sup(as_i("i,j")))) %>%
  compose(i = 2, j = 1, part = "body", value = as_paragraph(as_i("\U03B1"), as_sup(as_i("i,j")))) %>%
  compose(i = 3, j = 1, part = "body", value = as_paragraph(as_i("\U03B2"), as_sup(as_i("i,j")))) %>%
  compose(i = 4, j = 1, part = "body", value = as_paragraph(as_i("\U03B5"), as_sup(as_i("i,j")))) %>%
  compose(i = 1, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
  compose(i = 1, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("6"))) %>%
  compose(i = 1, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
  compose(i = 2, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("-2"))) %>%
  compose(i = 4, j = 5, part = "body", value = as_paragraph("1.5", "\U2A2F", "10", as_sup("-2"))) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # --- change headers labels--- #
  set_header_labels(values = list(
    Parameters = "Parameters",
    Range = "Range (m)",
    Mean = "Mean",
    Nugget = "Nugget",
    Sill = "Sill"
  )) %>%
  #- change the borders just for consistency with other tables -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  footnote(
    value = as_paragraph("NOTE: About ymax, the units of Mean, Nugget, and Sill are kg."),
    ref_symbols = NA
  ) %>%
  autofit()
```

@@

#-- (1) plot-level field map  --#
plot <-
  ggplot() +
  geom_sf(data = field_plot_sf) +
  geom_sf(data = ex_plot, fill = "green", size = 1) +
  coord_sf(expand = FALSE) +
  # theme_void() +
  ggtitle(TeX("$12 \\times 32$ plots")) +
  theme(plot.title = element_text(hjust = 0.5))

@@

#-- (2) create a map of subplots in a plot --##
subplots_inPlot <- 
  ggplot() +
  geom_sf(data = ex_plot, fill = "green") +
  geom_sf(data = ex_subplots, fill = NA, size = 1) +
  geom_sf(data = ex_subplots[2,], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  theme_void() +
  ggtitle(TeX("$4 \\times 1$ subplots")) +
  theme(plot.title = element_text(hjust = 0.5))

@@

#-- (3) create a map of cells in a subplot --#
cells_inSubplot <-
  ggplot() +
  geom_sf(data = ex_one_subplot, fill = "green", size = 1) +
  geom_sf(data = ex_cells, fill = NA) +
  geom_sf(data = ex_cells[2,], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  theme_void() +
  ggtitle(TeX("$6 \\times 6$ cells")) +
    theme(
    plot.title = element_text(hjust = 0.5)
  )

@@

#-- (4)put them on the same map --#
field_structure <-
  ggplot() +
  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE)+
  # /*----------------------------------*/
  #' ##  base maps
  # /*----------------------------------*/
  # --- plot level --- #
  annotation_custom(grob_plot,
    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1) +
  # --- subplot level --- #
  annotation_custom(grob_subplots_inPlot,
    xmin = 0.565, xmax = 0.665, ymin = 0.35, ymax = 0.7) + 
  # --- cell level --- #
  annotation_custom(grob_cells_inSubplot,
    xmin = 0.8, xmax = 0.8+0.2, ymin = 0.382, ymax = 0.382 +0.2) +
  #/*----------------------------------*/
  #' ## Add braces
  #/*----------------------------------*/
  # --- between plot and subplot --- #
  geom_brace(aes(c(0.43,0.43+0.1), c(0.353, 0.661)), color ="red", rotate = 270, inherit.data=F) +
  # --- between subplot and cell --- #
  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.381, 0.549)), color ="red", rotate = 270, inherit.data=F) +
  #/*----------------------------------*/
  #' ## add annotations
  #/*----------------------------------*/
  # --- annotation for plot --- #
  geom_segment(aes(x = 0.42, xend = 0.393, y = 0.60, yend = 0.515),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.015, label = "plot") +
  # --- annotation for subplot --- #
  geom_segment(aes(x = 0.7, xend = 0.64, y = 0.37, yend = 0.45),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot") +
  # --- annotation for cell --- #
  geom_segment(aes(x = 0.89, xend = 0.86, y = 0.349, yend = 0.394),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.89 + 0.015, y = 0.349 - 0.01, label = "cell") +
  # coord_sf(expand = FALSE) +
  theme_void() 
```

@@

```{r, dependson = "setup"}
field_Ndesign <-
  ggplot() +
  geom_sf(
    data = field_plot_sf,
    aes(fill = factor(rate)), size = 0,
    inherit.aes = FALSE,
  ) +
  scale_fill_viridis_d() +
  labs(fill = "Nitrogen rate\n  (kg/ha)") +
  theme_void()
```

@@

```{r, dependson = "setup"}
# === cell-level === #
vis_yield_cell <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = yield), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = "Yield Level\n  (kg/ha)") +
  theme_void()

# === subplot-level === #
vis_yield_subplot <-
  ggplot(field_subplot_sf) +
  geom_sf(aes(fill = yield), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = "Yield Level\n  (kg/ha)") +
  theme_void()
```

@@

```{r, dependson = "setup"}
# === cell-level === #
vis_optN_cell <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = opt_N), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = "EONR (kg/ha)") +
  theme_void()
```

@@

```{r, dependson = "setup"}
#### ==== ymax map ====####
field_ymax <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = ymax), size = 0) +
  scale_fill_viridis_c() +
  ggtitle("(1) ymax") +
  labs(fill = "kg/ha") +
  theme_void()

#### ==== alpha map ====####
field_alpha <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = alpha), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(TeX("(2)  $\\alpha$")) +
  # ggtitle(expression("(2) " ~alpha)) +
  theme_void() +
  theme(legend.title = element_blank())

#### ==== beta map ====####
field_beta <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = beta), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(TeX("(3)  $\\beta$")) +
  theme_void() +
  theme(legend.title = element_blank())

#### ==== m_error map ====#### (this should be m_error*det_yield, not just m_error)
# m_error_sf <-  left_join(field, coef_data_m, by="unique_cell_id")

field_m_error <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = yield_error), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(TeX("(4)  $\\epsilon$")) +
  labs(fill = "kg/ha") +
  theme_void()

# grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol=2, nrow=2)
```

@@

# /*-------------------------------------------------------*/
#' ## Organize the data
# /*-------------------------------------------------------*/
#--- for reporting the results of  yield prediction and EONR estimation ---#
report_res_allML <-
  rbind(res_forest_all_honest, res_CNN_all) %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF_stepwise", "CF_base"))] %>%
  .[, Model := factor(Model, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]

report_res_subsetML <-
  report_res_allML %>%
  .[Method != "CF_stepwise", ]
```

@@

rmse_y_all <-
  copy(report_res_allML) %>%
  .[Method %in% c("RF", "BRF", "CNN")]

# ==== Distribution of RMSE of predicted yields ====#
plot_dis_y <-
  copy(rmse_y_all) %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN"))] %>%
  ggplot() +
  geom_density(aes(x = rmse_y, fill = Method), alpha = 0.6) +
  facet_wrap(~Model, ncol = 1) +
  labs(x = "RMSE") +
  # labs(x = "Mean R-squared")+
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  )

@@

```{r}
fig_y_optN <-
  rmse_y_all[Method %in% c("RF", "BRF", "CNN")] %>%
  ggplot(aes(x = rmse_y, y = rmse_optN)) +
  geom_point(size = 0.5) +
  facet_grid(Model ~ Method) +
  # geom_smooth(method='lm', se=FALSE,  aes(colour="Regression line"), size=1) +
  # scale_colour_manual(values= "red") +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 1) +
  stat_regline_equation(
    # label.x.npc = "right",
    # label.y.npc = "top",
    label.x = 2150, label.y = 85,
    aes(label = ..rr.label..)
  ) +
  # geom_abline(slope=1, intercept=0, color="red")+
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 12, face = "bold"),
    legend.title = element_blank(),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  )

@@

# === Distribution of RMSE of EONR estimates === #

plot_dis_optN <-
  copy(report_res_subsetML) %>%
  .[Method %in% c("RF", "BRF", "CF_base"), ] %>%
  .[, Method := case_when(
    # Method == "CF_stepwise" ~ "CF-stepwise",
    Method == "CF_base" ~ "CF-base",
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF"
  )] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  # .[, Method:=factor(Method, levels = c("RF", "BRF", "CF-stepwise", "CF-base"))]%>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CF-base"))] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = rmse_optN, fill = Method), alpha = 0.7) +
  # scale_fill_viridis_d()+
  facet_wrap(~Model, ncol = 1) +
  # labs(x = expression(R^2))+
  labs(x = "RMSE (kg/ha)") +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  )

@@

# --- prepation --- #
table_optN_prep <-
  copy(report_res_subsetML) %>%
  .[, .(
    rmse_optN = mean(rmse_optN),
    pi_loss = mean(Mean)
  ), by = .(Method, Model)] %>%
  .[, `:=`(
    rmse_optN = format(round(rmse_optN, 1), nsmall = 1),
    pi_loss = format(round(pi_loss, 2), nsmall = 2)
  )] %>%
  dcast(Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA, blank5 = NA
  )] %>%
  .[, .(Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN, blank4, rmse_optN_CF_base, pi_loss_CF_base)]

@@

## Profit loss summary and distributions
```{r}
piLoss_density <-
  report_res_subsetML[Method != "CNN", ] %>%
  .[, Method := case_when(
    Method == "CF_base" ~ "CF-base",
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF"
  )] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CF-base"))] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = Mean, fill = Method), alpha = 0.5) +
  # scale_fill_viridis(discrete = TRUE, alpha=0.5) +
  # scale_fill_viridis_d()+
  # labs(x = expression(hat(pi)["loss"], " $/ha")))+
  labs(x = TeX("$\\hat{pi}_{loss}$ (\\$/ha)")) +
  facet_wrap(~Model, ncol = 1) +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  )
```

@@

figure_te <-
  here("Shared/Results/for_writing/dt_TEcomparison.rds") %>%
  readRDS() %>%
  .[, Method := case_when(
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF",
    Method == "CF_base" ~ "CF-base"
  )] %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CF-base"))] %>%
  ggplot() +
  geom_point(aes(x = true_tau_base, y = tau_base), size = 0.5) +
  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
  facet_grid(Treatment ~ Method) +
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  labs(y = "Estimated Treatment Effect (kg/ha)") +
  labs(x = "True Treatment Effect (kg/ha)") +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 12, face = "bold"),
    legend.title = element_blank(),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  )
```

@@

>>>>

knitr::opts_chunk$set(
  # cache = TRUE
  cache = FALSE
)
```
```{r packages, cache = FALSE, include = FALSE}
# === packages ===#
# --- data wrangling--- #
library(sf)
library(data.table)
library(tidyverse)

# --- figure making --- #
# library(extrafont)
library(ggbrace)
library(RColorBrewer)
library(patchwork)
library(ggplot2)
library(ggthemes)
library(viridis)
library(ggpubr)
library(gridExtra)
library(DiagrammeR)

# --- table making --- #
library(flextable)
library(ftExtra)
library(officer)
library(officedown)
library(modelsummary)
library(latex2exp)
```

@@

```{r}
theme_figure <- 
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    rect = element_blank(),
    text  = element_text(family = "Times New Roman")
    )

theme_dist <- 
  theme_bw()+
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom",
    text  = element_text(family = "Times New Roman")
    )

  # theme(    
  #   strip.text.x = element_text(size = 12, face = "bold"),
  #   legend.title = element_text(size = 12, face = "bold"),
  #   legend.text = element_text(size = 12, face = "bold"),
  #   legend.position = "bottom",
  #   text  = element_text(family = "Times New Roman")
  # )

set_flextable_defaults(
  font.family = "Times New Roman"
  )
```

@@

variogram_tb <-
  data.frame(
    Parameters = c("alpha_ij", "beta_ij", "ymax_ij", "varepsilon_ij"),
    Range = c(400, 400, 400, 400),
    Mean = c(-0.5, format(0), 12000, format(0)),
    Nugget = format(c(0, 0, 0, 0)),
    Sill = c(0.02, format(1, nsmall = 1), 2000000, 0.015)
  ) %>%
  flextable() %>%
  compose(i = 1, j = 1, part = "body", value = as_paragraph(as_i("\U03B1"), as_sub(as_i("i,j")))) %>%
  compose(i = 2, j = 1, part = "body", value = as_paragraph(as_i("\U03B2"), as_sub(as_i("i,j")))) %>%
  compose(i = 3, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sub(as_i("i,j")))) %>%
  compose(i = 4, j = 1, part = "body", value = as_paragraph(as_i("\U03B5"), as_sub(as_i("i,j")))) %>%
  compose(i = 1, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("-2"))) %>%
  compose(i = 3, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
  compose(i = 3, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("6"))) %>%
  compose(i = 4, j = 5, part = "body", value = as_paragraph("1.5", "\U2A2F", "10", as_sup("-2"))) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # --- change headers labels--- #
  set_header_labels(values = list(
    Parameters = "Parameters",
    Range = "Range (m)",
    Mean = "Mean",
    Nugget = "Nugget",
    Sill = "Sill"
  )) %>%
  #- change the borders just for consistency with other tables -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  footnote(
    value = as_paragraph("NOTE: Only in ", as_i("ymax"), " are consistent units of measurement used for Mean, Nugget, and Sill ", "(", as_i("kg"),")."),
    ref_symbols = NA
  ) %>%
  autofit()
```

@@

#-- (1) plot-level field map  --#

plot <-
  ggplot() +
  geom_sf(data = field_plot_sf) +
  geom_sf(data = ex_plot, fill = "green", size = 1) +
  coord_sf(expand = FALSE) +
  ggtitle("12 \u00D7 12 subplots") +
  # ggtitle(TeX("$12 \\times 32$ plots")) +
  theme_figure

@@

#-- (2) create a map of subplots in a plot --##
subplots_inPlot <- 
  ggplot() +
  geom_sf(data = ex_plot, fill = "green") +
  geom_sf(data = ex_subplots, fill = NA, size = 1) +
  geom_sf(data = ex_subplots[2,], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  theme_void() +
  # ggtitle(TeX("$4 \\times 1$ subplots")) +
  ggtitle("4 \u00D7 1 subplots") +
  theme_figure

@@

#-- (3) create a map of cells in a subplot --#
cells_inSubplot <-
  ggplot() +
  geom_sf(data = ex_one_subplot, fill = "green", size = 1) +
  geom_sf(data = ex_cells, fill = NA) +
  geom_sf(data = ex_cells[2,], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  theme_void() +
  # ggtitle(TeX("$6 \\times 6$ cells")) +
  ggtitle("6 \u00D7 6 cells") +
  theme_figure

@@

#-- (4)put them on the same map --#
field_structure <-
  ggplot() +
  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE)+
  # /*----------------------------------*/
  #' ##  base maps
  # /*----------------------------------*/
  # --- plot level --- #
  annotation_custom(grob_plot,
    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1) +
  # --- subplot level --- #
  annotation_custom(grob_subplots_inPlot,
    xmin = 0.565, xmax = 0.665, ymin = 0.35, ymax = 0.7) + 
  # --- cell level --- #
  annotation_custom(grob_cells_inSubplot,
    xmin = 0.8, xmax = 0.8+0.2, ymin = 0.382, ymax = 0.382 +0.2) +
  #/*----------------------------------*/
  #' ## Add braces
  #/*----------------------------------*/
  # --- between plot and subplot --- #
  geom_brace(aes(c(0.43,0.43+0.1), c(0.353, 0.661)), color ="red", rotate = 270, inherit.data=F) +
  # --- between subplot and cell --- #
  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.381, 0.549)), color ="red", rotate = 270, inherit.data=F) +
  #/*----------------------------------*/
  #' ## add annotations
  #/*----------------------------------*/
  # --- annotation for plot --- #
  geom_segment(aes(x = 0.42, xend = 0.383, y = 0.60, yend = 0.52),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.015, label = "plot", family="Times New Roman") +
  # --- annotation for subplot --- #
  geom_segment(aes(x = 0.7, xend = 0.64, y = 0.37, yend = 0.45),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot", , family="Times New Roman") +
  # --- annotation for cell --- #
  geom_segment(aes(x = 0.89, xend = 0.86, y = 0.349, yend = 0.394),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.89 + 0.015, y = 0.349 - 0.01, label = "cell", , family="Times New Roman") +
  theme_void()
```

@@

```{r, dependson = "setup"}
field_Ndesign <-
  ggplot() +
  geom_sf(
    data = field_plot_sf,
    aes(fill = factor(rate)), size = 0,
    inherit.aes = FALSE,
  ) +
  scale_fill_viridis_d() +
  labs(fill = "Nitrogen rate\n  (kg/ha)") +
  ggtitle("(a) Trial Design") +
  theme_figure
```

@@

```{r, dependson = "setup"}
# === subplot-level === #
vis_yield_subplot <-
  ggplot(field_subplot_sf) +
  geom_sf(aes(fill = yield), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = "Yield Level\n  (kg/ha)") +
  ggtitle("(b) Simulated Yield Level") +
  theme_figure
```

@@

```{r, dependson = "setup"}

@@

```{r, dependson = "setup"}
# === alpha map === #
field_alpha <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = alpha), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(expression("(1) " ~alpha)) +
  theme(legend.title = element_blank()) +
  theme_figure

# === beta map === #
field_beta <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = beta), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(expression("(2) " ~beta)) +
  theme(legend.title = element_blank()) +
  theme_figure

# === ymax map === #
field_ymax <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = ymax), size = 0) +
  scale_fill_viridis_c() +
  ggtitle("(3) ymax (kg/ha)") +
  theme(legend.title = element_blank()) +
  theme_figure

# === m_error map === #
# + this should be m_error*det_yield, not just m_error
# m_error_sf <-  left_join(field, coef_data_m, by="unique_cell_id")

field_m_error <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = yield_error), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(expression(paste("(4) " ~epsilon, " (kg/ha)"))) +
  theme(legend.title = element_blank()) +
  theme_figure

# === optN map === #
field_optN <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = opt_N), size = 0) +
  scale_fill_viridis_c() +
  ggtitle("(5) EONR (kg/ha)") +
  theme(legend.title = element_blank()) +
  theme_figure
```

@@

# /*-------------------------------------------------------*/
#' ## Organize the data
# /*-------------------------------------------------------*/
#--- for reporting the results of  yield prediction and EONR estimation ---#
res_allML <-
  rbind(res_forest_all_honest, res_CNN_all) %>%
  .[Method %in% c("RF", "BRF", "CNN", "CF_base")] %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF_base"))] %>%
  .[, Model := factor(Model, levels = c("aby", "abytt", "aabbyy", "aabbyytt"))]
```

@@

rmse_y_all <-
  copy(res_allML) %>%
  .[Method %in% c("RF", "BRF", "CNN")]

@@

```{r}
fig_y_optN <-
  rmse_y_all[Method %in% c("RF", "BRF", "CNN")] %>%
  ggplot(aes(x = rmse_y, y = rmse_optN)) +
  geom_point(size = 0.5) +
  facet_grid(Model ~ Method) +
  # geom_smooth(method='lm', se=FALSE,  aes(colour="Regression line"), size=1) +
  # scale_colour_manual(values= "red") +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 1) +
  stat_regline_equation(
    label.x = 2150, label.y = 85,
    aes(label = ..rr.label..)
  ) +
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 12, face = "bold"),
    legend.title = element_blank(),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  ) +
  theme_figure

@@

# === Distribution of RMSE of EONR estimates === #
plot_dis_optN <-
  copy(res_allML) %>%
  # .[Method %in% c("RF", "BRF", "CF_base"), ] %>%
  .[, Method := case_when(
    Method == "CF_base" ~ "CF-base",
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF",
    Method == "CNN" ~ "CNN"
  )] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  # .[, Method:=factor(Method, levels = c("RF", "BRF", "CF-stepwise", "CF-base"))]%>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF-base"))] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = rmse_optN, fill = Method), alpha = 0.7) +
  # scale_fill_viridis_d()+
  facet_wrap(~Model, ncol = 1) +
  # labs(x = expression(R^2))+
  labs(x = "RMSE (kg/ha)") +
  theme_dist

@@

# --- prepation --- #
table_optN_prep <-
  copy(res_allML) %>%
  .[, .(
    rmse_optN = mean(rmse_optN),
    pi_loss = mean(Mean)
  ), by = .(Method, Model)] %>%
  .[, `:=`(
    rmse_optN = format(round(rmse_optN, 1), nsmall = 1),
    pi_loss = format(round(pi_loss, 2), nsmall = 2)
  )] %>%
  dcast(Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA, blank5 = NA
  )] %>%
  .[, .(Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN, blank4, rmse_optN_CF_base, pi_loss_CF_base)]

@@

## Profit loss summary and distributions
```{r}
piLoss_density <-
  copy(res_allML) %>%
  .[, Method := case_when(
    Method == "CF_base" ~ "CF-base",
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF",
    Method == "CNN" ~ "CNN"
  )] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF-base"))] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = Mean, fill = Method), alpha = 0.7) +
  # scale_fill_viridis(discrete = TRUE, alpha=0.5) +
  # scale_fill_viridis_d()+
  labs(x = expression(paste(hat(pi)["loss"], " ($/ha)"))) +
  # labs(x = TeX("$\\hat{pi}_{loss}$ (\\$/ha)")) +
  facet_wrap(~Model, ncol = 1) +
  theme_dist

@@

figure_te <-
  here("Shared/Results/for_writing/dt_TEcomparison.rds") %>%
  readRDS() %>%
  .[, Method := case_when(
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF",
    Method == "CF_base" ~ "CF-base"
  )] %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CF-base"))] %>%
  ggplot() +
  geom_point(aes(x = true_tau_base, y = tau_base), size = 0.5) +
  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
  facet_grid(Treatment ~ Method) +
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  labs(y = "Estimated Treatment Effect (kg/ha)") +
  labs(x = "True Treatment Effect (kg/ha)") +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 12, face = "bold"),
    legend.title = element_blank(),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  ) +
  theme_figure
```

@@

# Preparation for exmaple field maps (one-time run)

```{r}
# source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")

# pCorn <- price_table[2, pCorn]
# pN <- price_table[2, pN]

# /*=================================================*/
#' # Field Data Sets
# /*=================================================*/
